Sparse spectral and $p$-finite element methods for partial differential equations on disk slices and trapeziums

### 2019-11-19 papers/disk-slices-and-trapeziums/revised/halfdisk.tex
resolving merge issues

\begin{figure}[t]
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityoflaplacian-w11-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityofhelmholtz-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityofbiharmonic-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
    	\caption{"Spy" plots of (differential) operator matrices, showing their sparsity. Left: the Laplace operator $\laplacewiii$. Centre: the weighted variable coefficient Helmholtz operator $\laplacewiii + k^2 \: T^{(0,0,0)\to(1,1,1)} \: V({J_x^{(0,0,0)}}^\top, {J_y^{(0,0,0)}}^\top) \: T_W^{(1,1,1)\to(0,0,0)}$ for $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 200$. Right: the biharmonic operator $\biharmonictwo$.}
        \label{fig:sparsity}
        \centering
\end{figure}

@@

% FIGURES
\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.3]{solution-poisson}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{solutionblocknorms-poisson-diskslice-alpha=0p2-beta=0p8}
        	%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$. Right: The norms of each block of the computed solution of the Poisson equation with the given right hand side functions. This demonstrates algebraic convergence with the rate dictated by the decay at the corners, with spectral convergence observed when the right-hand side vanishes to all orders.}
	\centering
	\label{fig:poisson}
\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\centering
	\includegraphics[scale=0.3]{solution-helmholtz-k=100-n=1500}
	%\label{fig:solution-helmholtz}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.5]{solutionblocknorms-helmholtz-diskslice-alpha=0p2-beta=0p8-N=196-k=20}
	\centering
        	%\label{fig:solutionblocknorms-helmholtz}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u + k^2 \: v \: u = f$ with zero boundary conditions with $f(x,y) = x(1-x^2-y^2)e^x$, $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 100$. Right: The norms of each block of the computed solution of the Helmholtz equation with the given right hand side functions, with $k=20$ and $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$.}
	\centering
	\label{fig:helmholtz}
\end{figure}

>>>>

\begin{figure}[t]
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityoflaplacian-w11} %-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityofhelmholtz} %-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityofbiharmonic} %-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
    	\caption{"Spy" plots of (differential) operator matrices, showing their sparsity. Left: the Laplace operator $\laplacewiii$. Centre: the weighted variable coefficient Helmholtz operator $\laplacewiii + k^2 \: T^{(0,0,0)\to(1,1,1)} \: V({J_x^{(0,0,0)}}^\top, {J_y^{(0,0,0)}}^\top) \: T_W^{(1,1,1)\to(0,0,0)}$ for $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 200$. Right: the biharmonic operator $\biharmonictwo$.}
        \label{fig:sparsity}
        \centering
\end{figure}

@@

% FIGURES
\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.3]{solution-poisson}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{solutionblocknorms-poisson} %-diskslice-alpha=0p2-beta=0p8}
        	%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$. Right: The norms of each block of the computed solution of the Poisson equation with the given right hand side functions. This demonstrates algebraic convergence with the rate dictated by the decay at the corners, with spectral convergence observed when the right-hand side vanishes to all orders.}
	\centering
	\label{fig:poisson}
\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\centering
	\includegraphics[scale=0.3]{solution-helmholtz-k=100-n=1500}
	%\label{fig:solution-helmholtz}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.5]{solutionblocknorms-helmholtz-k=20} %-diskslice-alpha=0p2-beta=0p8-N=196-k=20}
	\centering
        	%\label{fig:solutionblocknorms-helmholtz}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u + k^2 \: v \: u = f$ with zero boundary conditions with $f(x,y) = x(1-x^2-y^2)e^x$, $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 100$. Right: The norms of each block of the computed solution of the Helmholtz equation with the given right hand side functions, with $k=20$ and $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$.}
	\centering
	\label{fig:helmholtz}
\end{figure}
